My title

### 2024-01-20 outputs/paper/paper.qmd
Downloaded and saved the raw dataset in the inputs folder

The R programming language was used to conduct this analysis [@citeR], along with the `tidyverse` package [@citetidyverse].

>>>>

The R programming language was used to conduct this analysis [@citeR], along with the `janitor` [@citejanitor], `tidyverse` [@citetidyverse], and `opendatatoronto` [@citeopendatatoronto] packages.
